Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
Resolving some comments

\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
\jessiet{Make this subsection more concise?}
We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
Typically, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
We introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value (Definition \ref{def:consistent-prop}).

\jessiet{This paragraph feels a little redundant}
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}), which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
Most prior work on convex consistency dimension focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.

@@

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
  A loss and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
  \begin{align*}
    \E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
  \end{align*}
  % Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
  For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
  %\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
\end{definition}

@@

\begin{definition}[Consistent: property]\label{def:consistent-prop}
	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
  \end{equation}
  % where $D_x = \Pr[Y|X=x]$.
  We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
  Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me \#burn}}
  % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
  % In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
\end{definition}

@@

The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}.
\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
  Let $\P$ be a set of Lebesgue densities supported on the same set for all $p \in \P$.
  Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
  Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
  Then $\eliccvx(\lbar) \geq d+1$.
  \raft{Chain $\conscvx(\cdot)$ result}
\end{restatable}

@@

\begin{corollary}
  \label{cor:variance}
  Let $\P\subseteq\simplex$ for $\Y = \reals$, such that $\P$ is a set of Lebesgue densities with all $p \in \P$ having the same support, and there exists $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
  \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
  Then $\eliccvx(\Var)=2$.
  \raft{Chain $\conscvx(\cdot)$ result}
\end{corollary}
\begin{proof}
  For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
  Now for the lower bound.
  Without loss of generality, $\E_qY < \E_{q'}Y$.
  Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
  Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
  As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
  We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
  To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
  % and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
  By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
  Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
  As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
\end{proof}

@@

\begin{corollary}
  \label{cor:spectral-risks}
  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.\raft{Update}
  Then $\eliccvx(\CVaR_\alpha) \geq 2$.
  \raft{Chain $\conscvx(\cdot)$ result}
\end{corollary}
As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
We conjecture $\eliccvx(\CVaR_\alpha) \geq 3$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.

@@

When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex}.
Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.

@@

\begin{definition}[Calibrated: Quadrant 1]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
	A surrogate loss $L : \reals^d \times \Y \to \reals$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{$\P$-calibrated with respect to} $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \P: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \reals^d} \exploss{L}{u}{p}~.~
	\end{equation}
	We simply say $L$ is calibrated if $\P$ is understood from context.
\end{definition}

Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
%Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.).
%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
We give another definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.

For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}. 
%\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
Therefore, we use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.

The close connection between indirect elicitation and consistency was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).

@@

\begin{proposition}
	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are $\P$-calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are $\P$-calibrated via Definition~\ref{def:calibrated-finite}.
	\jessie{Change the order since we have forward refs?}
  %\btw{Okay if $\Gamma$ is empty}
\end{proposition}
\begin{proof}
$\implies$
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \P$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
%	
% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

>>>>

\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
Typically, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
We introduce a notion of consistency in which one is given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value (Definition \ref{def:consistent-prop}).

A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}), which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
Most prior work on convex consistency dimension focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.

@@

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
  A loss $L \in \L$ and link $(L,\psi)$ are \emph{$\D$-consistent} for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
  \begin{align*}
    \E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
  \end{align*}
  % Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
  For a given convex set $\P \subseteq \simplex$, we simply say $(L,\psi)$ is \emph{consistent} if it is $\D$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
  %\raft{Touched up to clarify the quantification over $\D$ \jessie{What I was trying to say, but better.}}
\end{definition}

@@

\begin{definition}[Consistent: property]\label{def:consistent-prop}
	Suppose we are given a loss $L \in \L$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
  \end{equation}
  % where $D_x = \Pr[Y|X=x]$.
  We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
  Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me \#burn}}
  % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
  % In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
\end{definition}

@@

The proof of the following Theorem is relegated to Appendix~\ref{app:pf-bayesrisklowerbound}.
\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}\btw{Old version for finite $\Y$ is in the NeurIPS 2020 submission; especially lots more detail on variance / norm / entropy examples}
  Let $\P$ be a set of Lebesgue densities supported on the same set for all $p \in \P$.
  Let $\Gamma:\P\to\reals^d$ satisfy Condition~\ref{cond:v-interior} for some $r\in\reals^d$.
  Let $L$ elicit $\Gamma$ such that $\lbar$ is non-constant on $\Gamma_r$.
  Then $\conscvx(\lbar)\geq \eliccvx(\lbar) \geq d+1$.
\end{restatable}

@@

\begin{corollary}
  \label{cor:variance}
  Let $\P\subseteq\simplex$ for $\Y = \reals$, such that $\P$ is a set of Lebesgue densities with all $p \in \P$ having the same support, and there exists $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$.
  \raft{Note to self: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
  Then $\conscvx(\Var) \geq \eliccvx(\Var)=2$.
\end{corollary}
\begin{proof}
  For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
  Now for the lower bound.
  Without loss of generality, $\E_qY < \E_{q'}Y$.
  Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
  Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
  As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
  We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
  To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
  % and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
  By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
  Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
  As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
\end{proof}

@@

\begin{corollary}
  \label{cor:spectral-risks}
  Let $\P\subseteq \P_q$ contain $p_1,p_2,p_3,p_2'$ such that $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$.\raft{Update}
  Then $\conscvx(\CVaR_\alpha) \geq \eliccvx(\CVaR_\alpha) \geq 2$.
\end{corollary}
As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
We conjecture $\eliccvx(\CVaR_\alpha) \geq 3$, which would be an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.

@@

When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\citep{tewari2007consistency,ramaswamy2016convex},notably in Quadrant 1.
Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.

@@

\begin{definition}[Calibrated: Quadrant 1]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
	A surrogate loss $L : \reals^d \times \Y \to \reals$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{$\P$-calibrated with respect to} $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \P: \inf_{u \in \reals^d : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \reals^d} \exploss{L}{u}{p}~.~
	\end{equation}
	We simply say $L$ is calibrated if $\P = \simplex$.
\end{definition}

Many works characterize calibrated surrogates for specific discrete target losses~\citep{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency}, including the canonical 0-1 loss for binary and multiclass classification.
%Moreover, \citet{steinwart2007compare} and \citet{steinwart2008support} generalize the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration for various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.).
%See~\citet[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
We give another definition of calibration which is a special case of calibration via~\citet{steinwart2008support}, and show it is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but can be applied in continuous estimation settings as well.
%
%For general settings, we introduce a notion of calibration that is a special case of calibration as introduced by~\citet[Definition 2.7]{steinwart2007compare} and~\citet[Chapter 3]{steinwart2008support}. 
%%\jessiet{I think we need to be careful how we present this; I'm not sure it's a new definition, though we seem to prove new results about it.}
%We will show that in discrete prediction settings, it is equivalent to the more commonplace definition given in Definition~\ref{def:calibrated-finite}.
We use this more general definition of calibration when proving statements about the relationship between consistency, calibration, and indirect elicitation.

The close connection between indirect elicitation and consistency was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.

@@

\begin{proposition}
	When $\R$ and $\Y$ are finite, a continuous loss and link $(L, \psi)$ are $\P$-calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if they are $\P$-calibrated via Definition~\ref{def:calibrated-finite}.
	%\jessie{Change the order since we have forward refs?}
  %\btw{Okay if $\Gamma$ is empty}
\end{proposition}
\begin{proof}
$\implies$
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \P$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
%	
% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.
